---
title: "Sex bias leadership results"
author: "Adrian Jaeggi"
date: "17 12 2021"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, include=FALSE, message=FALSE, warning=FALSE)
```


```{r loading}
 ## load relevant packages, set working directory, load saved model posteriors
library(brms)
library(rstan)
library(rethinking)
memory.limit(size=100000)
load("post_bgc.1_looped.robj")
load("post_mov.1_looped.robj")
load("post_mov.2_looped.robj")
load("post_bgc.4_looped.robj")

```

```{r post-processing posteriors}
# calculate phylogenetic signal for Model 1 (between-group conflict)
VarPhy.female<-post_bgc.1_looped$sd_phylo__muFemalebiased_Intercept
VarPhy.male<-post_bgc.1_looped$sd_phylo__muMalebiased_Intercept
VarSpec.female<-post_bgc.1_looped$sd_Genus_species__muFemalebiased_Intercept
VarSpec.male<-post_bgc.1_looped$sd_Genus_species__muMalebiased_Intercept
VarDistro<- pi^2/3
lambda.bgc.1_looped<- (VarPhy.female+VarPhy.male)/(VarPhy.female+VarPhy.male+VarSpec.female+VarSpec.male+VarDistro)

# calculate phylogenetic signal for Model 1 (movement)
VarPhy.female<-post_mov.1_looped$sd_phylo__muFemalebiased_Intercept
VarPhy.male<-post_mov.1_looped$sd_phylo__muMalebiased_Intercept
VarDistro<- pi^2/3
lambda.mov.1_looped<- (VarPhy.female+VarPhy.male)/(VarPhy.female+VarPhy.male+VarDistro)

# compute predicted probabilities for Model 1 (between-group conflict)
{    K <- 3 #number of character states used
  ns <- nrow(post_bgc.1_looped)
  n <- 1
  
  softmax2 <- function(x) {
    x <- max(x) - x
    exp(-x)/sum(exp(-x))
  }
  
  p.bgc1 <- list()
  
  for ( i in 1:n ) {
    p.bgc1[[i]] <- sapply( 1:K , function(k) {
      if ( k < K ) {
        ptemp <- post_bgc.1_looped[,k] 
      } else {
        ptemp <- rep(0,ns)
      }
      return(ptemp)
    })
    ## The values are converted to probabilities using the softmax function
    ## which ensures that the predicted values across categories sum to
    ## 100% probabilities.
    for ( s in 1:ns ) p.bgc1[[i]][s,] <- softmax2( p.bgc1[[i]][s,] )
  }
}
p_mean.bgc.1_looped <- sapply( 1:length(p.bgc1) , function(i) apply(p.bgc1[[i]],2,mean) )
p_HPDI.bgc.1_looped <- sapply( 1:length(p.bgc1) , function(i) apply(p.bgc1[[i]],2,HPDI, prob=0.95) )
pred_probs_bgc.1_looped<- cbind(p_mean.bgc.1_looped, p_HPDI.bgc.1_looped[c(1,3,5),], p_HPDI.bgc.1_looped[c(2,4,6),])

# probability of difference
diff.mf.bgc1<- p.bgc1[[1]][,2]-p.bgc1[[1]][,1]
diff.mu.bgc1<- p.bgc1[[1]][,2]-p.bgc1[[1]][,3]

# compute predicted probabilities for Model 1 (movememnt)
{    K <- 3 #number of character states used
  ns <- nrow(post_mov.1_looped)
  n <- 1
  
  softmax2 <- function(x) {
    x <- max(x) - x
    exp(-x)/sum(exp(-x))
  }
  
  p.mov1 <- list()
  
  for ( i in 1:n ) {
    p.mov1[[i]] <- sapply( 1:K , function(k) {
      if ( k < K ) {
        ptemp <- post_mov.1_looped[,k] 
      } else {
        ptemp <- rep(0,ns)
      }
      return(ptemp)
    })
    ## The values are converted to probabilities using the softmax function
    ## which ensures that the predicted values across categories sum to
    ## 100% probabilities.
    for ( s in 1:ns ) p.mov1[[i]][s,] <- softmax2( p.mov1[[i]][s,] )
  }
}
p_mean.mov.1_looped <- sapply( 1:length(p.mov1) , function(i) apply(p.mov1[[i]],2,mean) )
p_HPDI.mov.1_looped <- sapply( 1:length(p.mov1) , function(i) apply(p.mov1[[i]],2,HPDI, prob=0.95) )
pred_probs_mov.1_looped<- cbind(p_mean.mov.1_looped, p_HPDI.mov.1_looped[c(1,3,5),], p_HPDI.mov.1_looped[c(2,4,6),])

# probability of difference
diff.fm.mov1<- p.mov1[[1]][,1]-p.mov1[[1]][,2]
diff.fu.mov1<- p.mov1[[1]][,1]-p.mov1[[1]][,3]


```

Overall, we found that male-biased participation was most likely in intergroup conflict across mammals (Fig. 1, Model 1, see also supplement). Specifically, participation in intergroup conflicts was most likely to be male-biased (probability of male bias = `r round(pred_probs_bgc.1_looped,2)[2,1]`, 95% credible interval = `r round(pred_probs_bgc.1_looped,2)[2,2]` – `r round(pred_probs_bgc.1_looped,2)[2,3]`) rather than female-biased (`r round(pred_probs_bgc.1_looped,2)[1,1]`, `r round(pred_probs_bgc.1_looped,2)[1,2]` – `r round(pred_probs_bgc.1_looped,2)[1,3]`) or unbiased (`r round(pred_probs_bgc.1_looped,2)[3,1]`, `r round(pred_probs_bgc.1_looped,2)[3,2]` – `r round(pred_probs_bgc.1_looped,2)[3,3]`), with `r round(100*sum(diff.mf.bgc1>0)/length(diff.mf.bgc1),0)`%, `r round(100*sum(diff.mu.bgc1>0)/length(diff.mu.bgc1),0)`%, and `r round(100*sum(p.bgc1[[1]][,2]>0.33)/length(p.bgc1[[1]][,2]),0)`% confidence that the probability of male bias was higher than that of female bias, unbiased, and chance, respectively. In contrast, leadership in collective movement was more likely to be female-biased (`r round(pred_probs_mov.1_looped,2)[1,1]`, `r round(pred_probs_mov.1_looped,2)[1,2]` – `r round(pred_probs_mov.1_looped,2)[1,3]`), as opposed to male-biased (`r round(pred_probs_mov.1_looped,2)[2,1]`, `r round(pred_probs_mov.1_looped,2)[2,2]` – `r round(pred_probs_mov.1_looped,2)[2,3]`) or unbiased (`r round(pred_probs_mov.1_looped,2)[3,1]`, `r round(pred_probs_mov.1_looped,2)[3,2]` – `r round(pred_probs_mov.1_looped,2)[3,3]`), with the difference in probabilities supported with `r round(100*sum(diff.fm.mov1>0)/length(diff.fm.mov1),0)`% and `r round(100*sum(diff.fu.mov1>0)/length(diff.fu.mov1),0)`% confidence respectively, and female bias was higher than expected by chance with `r round(100*sum(p.mov1[[1]][,1]>0.33)/length(p.mov1[[1]][,1]),0)`% confidence There was weak phylogenetic signal in both models (mean Pagel's λ and 95% CI for intergroup conflict = `r round(mean(lambda.bgc.1_looped),2)`, `r round(HPDI(lambda.bgc.1_looped, prob=0.95)[1],2)` – `r round(HPDI(lambda.bgc.1_looped, prob=0.95)[2],2)`); for movement = `r round(mean(lambda.mov.1_looped),2)`, `r round(HPDI(lambda.mov.1_looped, prob=0.95)[1],2)` – `r round(HPDI(lambda.mov.1_looped, prob=0.95)[2],2)`), somewhat reduced by strong priors on variance components, implying that this typical mammalian pattern of male-biased participation in intergroup conflict and female-biased leadership in movement also applies to some extent to ancestral species.

These results did not change fundamentally when adding sexual dimorphism and resource defensibility as predictor variables (Model 2, see supplement for details); the only reasonably well-supported association was that male-biased leadership in movements was less likely when food was defendable vs non-defendable (mean odd’s ratio (OR) = `r round(mean(exp(post_mov.2_looped$b_muMalebiased_Food_resource_defendable)),2)`, 95% CI = `r round(HPDI(exp(post_mov.2_looped$b_muMalebiased_Food_resource_defendable), prob=0.95)[1],2)` – `r round(HPDI(exp(post_mov.2_looped$b_muMalebiased_Food_resource_defendable), prob=0.95)[2],2)`, probabilityOR<1 = `r round(100*sum(post_mov.2_looped$b_muMalebiased_Food_resource_defendable<0)/nrow(post_mov.2_looped),0)`%). Results did also not differ qualitatively between primates and non-primates (Model 3, see supplement for details). In terms of the link between sex bias across contexts (Model 4), the probability of male-biased participation in intergroup conflict was strongly reduced in species with female-biased leadership during movement (mean OR = `r round(mean(exp(post_bgc.4_looped$b_muMalebiased_Movement_zero_center.factFemaleMbiased)),2)`, 95% CI = `r round(HPDI(exp(post_bgc.4_looped$b_muMalebiased_Movement_zero_center.factFemaleMbiased), prob=0.95)[1],2)` – `r round(HPDI(exp(post_bgc.4_looped$b_muMalebiased_Movement_zero_center.factFemaleMbiased), prob=0.95)[2],2)`; probability OR<1 = `r round(100*sum(post_bgc.4_looped$b_muMalebiased_Movement_zero_center.factFemaleMbiased<0)/nrow(post_bgc.4_looped),0)`%), though other associations were much more uncertain (e.g. greater female bias in intergroup conflict when there is female bias in movement, OR = `r round(mean(exp(post_bgc.4_looped$b_muFemalebiased_Movement_zero_center.factFemaleMbiased)),2)`, 95% CI = `r round(HPDI(exp(post_bgc.4_looped$b_muFemalebiased_Movement_zero_center.factFemaleMbiased), prob=0.95)[1],2)` – `r round(HPDI(exp(post_bgc.4_looped$b_muFemalebiased_Movement_zero_center.factFemaleMbiased), prob=0.95)[2],2)`; probability OR>1 = `r round(100*sum(post_bgc.4_looped$b_muFemalebiased_Movement_zero_center.factFemaleMbiased>0)/nrow(post_bgc.4_looped),0)`%; see supplement for complete results, Fig. 2). 

```` {r figure}
library(ape)
library(phytools)
library(wesanderson)
library(TreeTools)

# compute consensus tree to get tip order to be plotted
# for some reason, the order of tip labels only updates after writing the tree -> write and re-read
cons.tree<- consensus.edges(ntrees)
write.tree(cons.tree, "PhyForFigure.tre")
cons.tree<- read.tree("PhyForFigure.tre")


# create vector of traits per species
t.mov<- table(d2$Genus_species, d2$Movement_zero_center.fact)
t2.mov<- t.mov[ order(match(rownames(t.mov), cons.tree$tip.label)), ]
t.bgc<- table(d2$Genus_species, d2$Between.Conflict_zero_center.fact)
t2.bgc<- t.bgc[ order(match(rownames(t.bgc), cons.tree$tip.label)), ]

tiff("Figure 1.tif", compression="lzw", height=6.0, width=6.0, units="cm", res=600, pointsize=5)

# plot trees
densityTree(ntrees,type="cladogram", show.axis=FALSE, fsize=0.5, color=wes_palettes$Moonrise2[4], offset=0.5, lwd=1)

## add colored boxes for character states to tree
for(i in 1:nrow(t2.mov)){if(t2.mov[i,"Male-biased"]>0) points(x=-1, y=0+i, pch=15, cex=0.7, col=wes_palettes$Moonrise2[1])}
for(i in 1:nrow(t2.mov)){if(t2.mov[i,"Unbiased"]>0) points(x=-1, y=0+i, pch=15, cex=0.7, col=wes_palettes$Moonrise2[2])}
for(i in 1:nrow(t2.mov)){if(t2.mov[i,"Female-biased"]>0) points(x=-1, y=0+i, pch=15, cex=0.7, col=wes_palettes$Moonrise2[3])}

for(i in 1:nrow(t2.bgc)){if(t2.bgc[i,"Male-biased"]>0) points(x=-3, y=0+i, pch=15, cex=0.7, col=wes_palettes$Moonrise2[1])}
for(i in 1:nrow(t2.bgc)){if(t2.bgc[i,"Unbiased"]>0) points(x=-3, y=0+i, pch=15, cex=0.7, col=wes_palettes$Moonrise2[2])}
for(i in 1:nrow(t2.bgc)){if(t2.bgc[i,"Female-biased"]>0) points(x=-3, y=0+i, pch=15, cex=0.7, col=wes_palettes$Moonrise2[3])}

## create inset plot
par(fig = c(0.1, 0.5, 0.1, 0.45), mar = c(2, 2, 3, 2), new = T)

# leadership probabilities for typical mammal
plot(c(0,1)~c(1,2), col="white", xaxt="n", yaxt="n", ylab="Probability of sex bias", xlab="", main="", xlim=c(0.5,2.5), cex.lab=0.75, cex.axis=0.75)
axis(1, at=c(1,2), labels=FALSE)
axis(2, at=c(0,0.2,0.4,0.6,0.8,1), labels=FALSE)
text(x=c(1,2), xpd=NA, adj=1, srt=45, labels=c("Movement", "Intergroup\n conflict"), y=-0.2, cex=0.75)
text(y=c(0,0.2,0.4,0.6,0.8,1), adj=0.15, xpd=NA, labels=c("0.0", "0.2", "0.4", "0.6", "0.8", "1.0"), x=0, cex=0.75)
text(y=0.5, xpd=NA, labels="Probability of sex bias", srt=90, x=-0.2, cex=0.75)

points(0.75, pred_probs_mov.1.cons["Male-biased","mean"], pch=16, col=wes_palettes$Moonrise2[1], cex=2)
arrows(0.75, pred_probs_mov.1.cons["Male-biased","lwr95"], 0.75, pred_probs_mov.1.cons["Male-biased","upr95"], length=0, angle=90, col=wes_palettes$Moonrise2[1], lwd=2)
points(1, pred_probs_mov.1.cons["Unbiased","mean"], pch=16, col=wes_palettes$Moonrise2[2], cex=2)
arrows(1, pred_probs_mov.1.cons["Unbiased","lwr95"], 1, pred_probs_mov.1.cons["Unbiased","upr95"], length=0, angle=90, col=wes_palettes$Moonrise2[2], lwd=2)
points(1.25, pred_probs_mov.1.cons["Female-biased","mean"], pch=16, col=wes_palettes$Moonrise2[3], cex=2)
arrows(1.25, pred_probs_mov.1.cons["Female-biased","lwr95"], 1.25, pred_probs_mov.1.cons["Female-biased","upr95"], length=0, angle=90, col=wes_palettes$Moonrise2[3], lwd=2)

points(1.75, pred_probs_bgc.1.cons["Male-biased","mean"], pch=16, col=wes_palettes$Moonrise2[1], cex=2)
arrows(1.75, pred_probs_bgc.1.cons["Male-biased","lwr95"], 1.75, pred_probs_bgc.1.cons["Male-biased","upr95"], length=0, angle=90, col=wes_palettes$Moonrise2[1], lwd=2)
points(2, pred_probs_bgc.1.cons["Unbiased","mean"], pch=16, col=wes_palettes$Moonrise2[2], cex=2)
arrows(2, pred_probs_bgc.1.cons["Unbiased","lwr95"], 2, pred_probs_bgc.1.cons["Unbiased","upr95"], length=0, angle=90, col=wes_palettes$Moonrise2[2], lwd=2)
points(2.25, pred_probs_bgc.1.cons["Female-biased","mean"], pch=16, col=wes_palettes$Moonrise2[3], cex=2)
arrows(2.25, pred_probs_bgc.1.cons["Female-biased","lwr95"], 2.25, pred_probs_bgc.1.cons["Female-biased","upr95"], length=0, angle=90, col=wes_palettes$Moonrise2[3], lwd=2)

par(fig = c(0,1,0,1), new=FALSE)

# add legend
par(xpd=NA)
legend(x=0.1, y=0.55, fill=c(wes_palettes$Moonrise2[1],wes_palettes$Moonrise2[2],wes_palettes$Moonrise2[3]), border=NA, legend=c("Male-biased", "Unbiased", "Female-biased"), bty="n")

dev.off()

````

